The development of infants' responses to mispronunciations: A Meta-Analysis

### 2020-12-08 VonHolzenBergmann_MPMetaAnalysis.Rmd
final proofs

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list (see Figure \@ref(fig:PRISMA-image) for an overview of the selection process). This process yielded 110 items. We then used the Google Scholar search engine to search for papers citing the original @Swingley2000 publication. This search was conducted on 22 September, 2017 and yielded 288 results. From this combined list of 398 records we removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (*n* = `r length(unique(descriptive_dat$short_cite))`) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table \@ref(tab:SummaryTable) provides an overview of all papers included in the present meta-analysis.

@@

  jpeg(filename = "figures/Figure_2_Funnel_Plots_Object_Identification.jpg", 
       width = 600, height = 400, units = "px")

@@

```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=8, fig.cap="Panel a: Effect sizes for correct pronunciations (yellow) and mispronunciations (blue) by participant age. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) by participant age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

  jpeg(filename = "figures/Figure_3_AgeEffect.jpg", 
       width = 500, height = 900, units = "px")

@@

```{r Vocabdescribe1, echo = FALSE, fig.width=7,fig.height=4.5, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (yellow), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (pink).", results="hide"}
#how did vocabulary collection change over time?

@@

  jpeg(filename = "figures/Figure_4_Vocab_findings.jpg", 
       width = 550, height = 300, units = "px")

@@

  jpeg(filename = "figures/Figure_5_Number_of_Features.jpg", 
       width = 500, height = 300, units = "px")

@@

  jpeg(filename = "figures/Figure_6_Misp_Position.jpg", 
       width = 500, height = 300, units = "px")

@@

```{r PlotMispType, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

  jpeg(filename = "figures/Figure_7_CV.jpg",
       width = 500, height = 800, units = "px")

@@

```{r PlotCVEffectLang, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

  jpeg(filename = "figures/Figure_8_LangCV.jpg",
       width = 500, height = 900, units = "px")

@@

```{r PlotDistOverlap, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

  jpeg(filename = "figures/Figure_9_Distractor_Overlap.jpg",
       width = 500, height = 800, units = "px")

@@

```{r PlotPostNameCondAge, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (yellow), 2001 to 3000 ms (blue), and 3001 ms or greater (pink). Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing. Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
dat$condition_label <- ifelse(dat$condition==1, "Correct", "Mispronunciation")
dat$post_size <- ifelse(dat$post_nam_dur <= 2, "2000 ms or less",
                       ifelse(dat$post_nam_dur > 2 & dat$post_nam_dur <= 3, "2001-3000 ms", "3001 ms or greater"))
dat$post_size <- factor(dat$post_size, levels = c("2000 ms or less", "2001-3000 ms", "3001 ms or greater"))
dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "post_size", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
dat.c <- subset(dat.cm, is_correct == 1)
dat.m <- subset(dat.cm, is_mp == 1)
dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "post_size", "mean_age_1", "n_1"))
dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
p.MS <- ggplot(dat.cm, aes(post_size, Misp_sensitivity, fill = post_size)) + 
  #facet_grid(.~post_size)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  #scale_fill_grey()+
    scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")
p.AGE <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = post_size)) + 
    #facet_grid(.~post_size)+
  geom_point(aes(size = weight),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  #scale_colour_grey()+
    scale_color_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")
lay <- rbind(c(1), c(2))
#lay <- rbind(c(1,2))
  jpeg(filename = "figures/Figure_10_Post_name_size.jpg", 
       width = 600, height = 800, units = "px")

@@

```{r PlotWithinCondDVbaseline, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (yellow), Post vs. Pre (blue), and Difference Score (pink). Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}

@@

#lay <- rbind(c(1,2))
  jpeg(filename = "figures/Figure_11_Dependent_variable.jpg", 
       width = 500, height = 350, units = "px")

@@

>>>>

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list (see Figure \@ref(fig:PRISMA-image) for an overview of the selection process). This process yielded 110 items. We then used the Google Scholar search engine to search for papers citing the original @Swingley2000 publication. This search was conducted on 22 September, 2017 and yielded 288 results. From this combined list of 398 records we removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (*n* = `r length(unique(descriptive_dat$short_cite))`) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished report. We will refer to these items collectively as papers. Table \@ref(tab:SummaryTable) provides an overview of all papers included in the present meta-analysis.

@@

  jpeg(filename = "figures/Figure_2_Funnel_Plots_Object_Identification.jpg", 
       width = 1600, height = 800, units = "px", res = 300)

@@

```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=8, fig.cap="Panel a: Effect sizes for correct pronunciations (light orange, light grey) and mispronunciations (dark purple, black) by participant age. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) by participant age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

  jpeg(filename = "figures/Figure_3_AgeEffect.jpg", 
       width = 1450, height = 1800, units = "px", res = 300)

@@

```{r Vocabdescribe1, echo = FALSE, fig.width=7,fig.height=4.5, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (light orange, light grey), did measure vocabulary and was reported to predict mispronunciation sensitivity (dark purple, black), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (dark orange, dark grey).", results="hide"}
#how did vocabulary collection change over time?

@@

  jpeg(filename = "figures/Figure_4_Vocab_findings.jpg", 
       width = 2200, height = 1200, units = "px", res = 300)

@@

  jpeg(filename = "figures/Figure_5_Number_of_Features.jpg", 
       width = 1800, height = 1200, units = "px", res = 300)

@@

  jpeg(filename = "figures/Figure_6_Misp_Position.jpg", 
       width = 1800, height = 1200, units = "px", res = 300)

@@

```{r PlotMispType, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant (light orange, light grey) and vowel (dark purple, black) mispronunciations by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

  jpeg(filename = "figures/Figure_7_CV.jpg",
       width = 1450, height = 1800, units = "px", res = 300)

@@

```{r PlotCVEffectLang, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant (light orange, light grey) and vowel (dark purple, black) mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

  jpeg(filename = "figures/Figure_8_LangCV.jpg",
       width = 1450, height = 2200, units = "px", res = 300)

@@

```{r PlotDistOverlap, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap (dark purple, black) or no overlap (light orange, light grey) by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

  jpeg(filename = "figures/Figure_9_Distractor_Overlap.jpg",
       width = 1600, height = 1800, units = "px", res = 300)

@@

```{r PlotPostNameCondAge, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (light orange, light grey), 2001 to 3000 ms (dark purple, black), and 3001 ms or greater (dark orange, dark grey). Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing. Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
dat$condition_label <- ifelse(dat$condition==1, "Correct", "Mispronunciation")
dat$post_size <- ifelse(dat$post_nam_dur <= 2, "< 2000 ms",
                       ifelse(dat$post_nam_dur > 2 & dat$post_nam_dur <= 3, "2001-3000 ms", "> 3001 ms"))
dat$post_size <- factor(dat$post_size, levels = c("< 2000 ms", "2001-3000 ms", "> 3001 ms"))
dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "post_size", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
dat.c <- subset(dat.cm, is_correct == 1)
dat.m <- subset(dat.cm, is_mp == 1)
dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "post_size", "mean_age_1", "n_1"))
dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
p.MS <- ggplot(dat.cm, aes(post_size, Misp_sensitivity, fill = post_size)) + 
  #facet_grid(.~post_size)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  #scale_fill_grey()+
    scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")
p.AGE <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = post_size)) + 
    #facet_grid(.~post_size)+
  geom_point(aes(size = weight),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  #scale_colour_grey()+
    scale_color_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")
lay <- rbind(c(1), c(2))
#lay <- rbind(c(1,2))
  jpeg(filename = "figures/Figure_10_Post_name_size.jpg", 
       width = 2200, height = 2200, units = "px", res = 300)

@@

```{r PlotWithinCondDVbaseline, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (light orange, light grey) and Baseline corrected (dark purple, black). Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}

@@

#lay <- rbind(c(1,2))
  jpeg(filename = "figures/Figure_11_Dependent_variable.jpg", 
       width = 1800, height = 1200, units = "px", res = 300)

@@

---
nocite: |
  @Ren, @Bergelson2017, @DelleLuche2015, @Durrant2014, @Hohle2006, @Swingley2003, @Tao2013, @Tao2012, @VanderFeest2016, @Wewalaarachchi2017, @White2011a, @Zesiger2011
---

### 2020-12-08 VonHolzenBergmann_MPMetaAnalysis.tex
final proofs

The authors would like to thank Emelyne Gaudichau for valuable assistance in entering data. The data, analysis scripts, and RMarkdown file used in this study to create this manuscript are available on the Open Science Framework (\url{https://osf.io/rvbjs/}). Katie Von Holzen was supported by the Agence Nationale de la Recherche (ANR-13-BSH2-0004) and by training grant DC-00046 from the National Institute of Deafness and Communicative Disorders of the National Institutes of Health. Christina Bergmann was supported by H2020 European Research Council Marie Skłodowska-Curie grant No 660911; the Département d'Etudes Cognitives (DEC) ANR-17-EURE-0017, the Berkeley Initiative for Transparency in the Social Sciences, a program of the Center for Effective Global Action (CEGA), with support from the Laura and John Arnold Foundation. The authors each declare that they have no conflict of interest.

@@

Ren \& Morgan (in press) & gray paper & 19 & None & unfam & none & 1 & O, C & C & 8\\

@@

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list (see Figure \ref{fig:PRISMA-image} for an overview of the selection process). This process yielded 110 items. We then used the Google Scholar search engine to search for papers citing the original Swingley and Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. From this combined list of 398 records we removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (\emph{n} = 32) consisted of 27 journal articles, 1 proceedings paper, 2 theses, and 2 unpublished reports. We will refer to these items collectively as papers. Table \ref{tab:SummaryTable} provides an overview of all papers included in the present meta-analysis.

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMPEffect-1.pdf}
\caption{\label{fig:PlotMPEffect}Panel a: Effect sizes for correct pronunciations (yellow) and mispronunciations (blue) by participant age. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) by participant age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/Vocabdescribe1-1.pdf}
\caption{\label{fig:Vocabdescribe1}Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (yellow), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (pink).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMispType-1.pdf}
\caption{\label{fig:PlotMispType}Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotCVEffectLang-1.pdf}
\caption{\label{fig:PlotCVEffectLang}Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotDistOverlap-1.pdf}
\caption{\label{fig:PlotDistOverlap}Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotPostNameCondAge-1.pdf}
\caption{\label{fig:PlotPostNameCondAge}Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (yellow), 2001 to 3000 ms (blue), and 3001 ms or greater (pink). Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing. Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotWithinCondDVbaseline-1.pdf}
\caption{\label{fig:PlotWithinCondDVbaseline}Effect sizes for the different types of dependent variables calculated: Post (yellow), Post vs.~Pre (blue), and Difference Score (pink). Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error.}
\end{figure}

@@

@@

@@

@@

@@

@@

@@

@@

\leavevmode\hypertarget{ref-VonHolzen2019}{}%
Von Holzen, K., \& Bergmann, C. (2019). Infant Mispronunciation Sensitivity Meta-Analysis (InMisSens). \url{https://doi.org/10.31234/osf.io/dze29}

@@

@@

>>>>

The authors would like to thank Emelyne Gaudichau for valuable assistance in entering data. The data, analysis scripts, and RMarkdown file used in this study to create this manuscript are available on the Open Science Framework (Von Holzen \& Bergmann, 2019; \url{https://osf.io/rvbjs/}). Katie Von Holzen was supported by the Agence Nationale de la Recherche (ANR-13-BSH2-0004) and by training grant DC-00046 from the National Institute of Deafness and Communicative Disorders of the National Institutes of Health. Christina Bergmann was supported by H2020 European Research Council Marie Skłodowska-Curie grant No 660911; the Département d'Etudes Cognitives (DEC) ANR-17-EURE-0017, the Berkeley Initiative for Transparency in the Social Sciences, a program of the Center for Effective Global Action (CEGA), with support from the Laura and John Arnold Foundation. The authors each declare that they have no conflict of interest.

@@

Ren \& Morgan (in press) & paper & 19 & None & unfam & none & 1 & O, C & C & 8\\

@@

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list (see Figure \ref{fig:PRISMA-image} for an overview of the selection process). This process yielded 110 items. We then used the Google Scholar search engine to search for papers citing the original Swingley and Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. From this combined list of 398 records we removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (\emph{n} = 32) consisted of 28 journal articles, 1 proceedings paper, 2 theses, and 1 unpublished report. We will refer to these items collectively as papers. Table \ref{tab:SummaryTable} provides an overview of all papers included in the present meta-analysis.

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMPEffect-1.pdf}
\caption{\label{fig:PlotMPEffect}Panel a: Effect sizes for correct pronunciations (light orange, light grey) and mispronunciations (dark purple, black) by participant age. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) by participant age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/Vocabdescribe1-1.pdf}
\caption{\label{fig:Vocabdescribe1}Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (light orange, light grey), did measure vocabulary and was reported to predict mispronunciation sensitivity (dark purple, black), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (dark orange, dark grey).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMispType-1.pdf}
\caption{\label{fig:PlotMispType}Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant (light orange, light grey) and vowel (dark purple, black) mispronunciations by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotCVEffectLang-1.pdf}
\caption{\label{fig:PlotCVEffectLang}Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant (light orange, light grey) and vowel (dark purple, black) mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotDistOverlap-1.pdf}
\caption{\label{fig:PlotDistOverlap}Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap (dark purple, black) or no overlap (light orange, light grey) by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotPostNameCondAge-1.pdf}
\caption{\label{fig:PlotPostNameCondAge}Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (light orange, light grey), 2001 to 3000 ms (dark purple, black), and 3001 ms or greater (dark orange, dark grey). Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing. Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotWithinCondDVbaseline-1.pdf}
\caption{\label{fig:PlotWithinCondDVbaseline}Effect sizes for the different types of dependent variables calculated: Post (light orange, light grey) and Baseline corrected (dark purple, black). Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error.}
\end{figure}

@@

\leavevmode\hypertarget{ref-Bergelson2017}{}%
Bergelson, E., \& Swingley, D. (2018). Young infants ' word comprehension given an unfamiliar talker or altered pronunciations. \emph{Child Development}, \emph{89}(5), 1567--1576. \url{https://doi.org/10.1111/cdev.12888}

@@

\leavevmode\hypertarget{ref-DelleLuche2015}{}%
Delle Luche, C., Durrant, S., Poltrock, S., \& Floccia, C. (2015). A methodological investigation of the Intermodal Preferential Looking paradigm: Methods of analyses, picture selection and data rejection criteria. \emph{Infant Behavior and Development}, \emph{40}, 151--172. \url{https://doi.org/10.1016/j.infbeh.2015.05.005}

\leavevmode\hypertarget{ref-Durrant2014}{}%
Durrant, S., Delle Luche, C., Cattani, A., \& Floccia, C. (2015). Monodialectal and multidialectal infants ' representation of familiar words. \emph{Journal of Child Language}, \emph{42}(2), 447--462. \url{https://doi.org/10.1017/S0305000914000063}

@@

\leavevmode\hypertarget{ref-VanderFeest2016}{}%
Feest, S. V. H. van der, \& Johnson, E. K. (2016). Input Driven Differences in Toddler's Perception of a Disappearing Phonological Contrast. \emph{Language Acquisition}, \emph{23}(2), 89--111. \url{https://doi.org/10.1080/10489223.2015.1047096}

@@

\leavevmode\hypertarget{ref-Hohle2006}{}%
Höhle, B., Vijver, R. van de, \& Weissenborn, J. (2006). Word processing at 19 months and its relation to language performance at 30 months: A retrospective analysis of data from German learning children. \emph{International Journal of Speech-Language Pathology}, \emph{8}(4), 356--363. \url{https://doi.org/10.1080/14417040600970614}

@@

\leavevmode\hypertarget{ref-Ren}{}%
Ren, J., Cohen-Priva, U., \& Morgan, J. L. (2019). Underspecification in toddlers' and adults' lexical representations. \emph{Cognition}, \emph{193}. \url{https://doi.org/10.1016/j.cognition.2019.06.003}

@@

\leavevmode\hypertarget{ref-Swingley2003}{}%
Swingley, D. (2003). Phonetic detail in the developing lexicon. \emph{Language and Speech}, \emph{46}(2-3), 265--294. \url{https://doi.org/10.1177/00238309030460021001}

@@

\leavevmode\hypertarget{ref-Tao2013}{}%
Tao, Y., \& Qinmei, X. (2013). Phonological specificity of lexical tones in 12-month-old chinese-speaking infants. \emph{Acta Psychologica Sinica}, \emph{45}(10), 1111--1118. \url{https://doi.org/10.3724/SP.J.1041.2013.01111}

\leavevmode\hypertarget{ref-Tao2012}{}%
Tao, Y., Qinmei, X., \& Plunkett, K. (2012). Phonological specificity of tones in early lexical representation at 16 months of age. \emph{Acta Psychologica Sinica}, \emph{44}(8), 1066--1074. \url{https://doi.org/10.3724/SP.J.1041.2012.01066}

@@

@@

\leavevmode\hypertarget{ref-Wewalaarachchi2017}{}%
Wewalaarachchi, T. D., Wong, L. H., \& Singh, L. (2017). Vowels, consonants, and lexical tones: Sensitivity to phonological variation in monolingual Mandarin and bilingual English -- Mandarin toddlers. \emph{Journal of Experimental Child Psychology}, \emph{159}, 16--33. \url{https://doi.org/10.1016/j.jecp.2017.01.009}

\leavevmode\hypertarget{ref-White2011a}{}%
White, K. S., \& Aslin, R. N. (2011). Adaptation to novel accents by toddlers. \emph{Developmental Science}, \emph{14}(2), 372--384. \url{https://doi.org/10.1111/j.1467-7687.2010.00986.x}

@@

\leavevmode\hypertarget{ref-Zesiger2011}{}%
Zesiger, P., \& Jöhr, J. (2011). Les représentations phonologiques des mots chez le jeune enfant. \emph{Enfance}, \emph{3}, 293--309.
